---
title: "``MachineShop::calibration``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(MachineShop)
```


 Model Calibration

#### Description

Calculate calibration estimates from observed and predicted responses.

#### Usage
<pre><code>

Calibration(...)
calibration(x, y = NULL, breaks = 10, ...)

</code></pre>
####Arguments

... named or unnamed calibration output to combine together with the Calibration
constructor.
x observed responses or Resamples object of observed and predicted responses.
y predicted responses.
breaks value defining the response variable bins within which to calculate observed
mean values. May be specified as a number of bins, a vector of breakpoints,
or NULL to fit smooth curves with splines for survival responses and loess for
others.



#### Examples
```{r}

library(survival)
library(MASS)
res <- resample(Surv(time, status != 2) ~ sex + age + year + thickness + ulcer,
data = Melanoma, model = GBMModel,
control = CVControl(times = 365 * c(2, 5, 10)))
cal <- calibration(res)
plot(cal)
```

#### Value

Calibration class object that inherits from data.frame.
See Also
response, predict, resample, plot
CForestModel 15
