---
title: "``MachineShop::CForestModel ``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(MachineShop)
```



Conditional Random Forest Model

#### Description

An implementation of the random forest and bagging ensemble algorithms utilizing conditional
inference trees as base learners.

#### Usage
<pre><code>

CForestModel(teststat = c("quad", "max"), testtype = c("Univariate",
"Teststatistic", "Bonferroni", "MonteCarlo"), mincriterion = 0,
ntree = 500, mtry = 5, replace = TRUE, fraction = 0.632)

</code></pre>
####Arguments

teststat character specifying the type of the test statistic to be applied.
testtype character specifying how to compute the distribution of the test statistic.
mincriterion value of the test statistic that must be exceeded in order to implement a split.
ntree number of trees to grow in a forest.
mtry number of input variables randomly sampled as candidates at each node for
random forest like algorithms.
replace logical indicating whether sampling of observations is done with or without replacement.
fraction fraction of number of observations to draw without replacement (only relevant
if replace = FALSE).


#### Value

MLModel class object.
See Also
cforest, fit, resample, tune

#### Examples
```{r}

library(MASS)
fit(medv ~ ., data = Boston, model = CForestModel())
```

Details
Response Types: factor, numeric, Surv
Automatic Tuning Grid Parameters: mtry
Supplied arguments are passed to cforest_control. Further model details can be found in the
source link below.
16 confusion
