---
title: "``MachineShop::confusion ``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(MachineShop)
```


Confusion Matrix

#### Description

Calculate confusion matrices of predicted and observed responses.

#### Usage
<pre><code>

Confusion(...)
confusion(x, y = NULL, cutoff = 0.5, ...)

</code></pre>
####Arguments

* ... named or unnamed confusion output to combine together with the Confusion constructor.
* x factor of observed responses or Resamples object of observed and predicted responses.
* y predicted responses.
* cutoff threshold above which binary factor probabilities are classified as events and below which survival probabilities are classified. If NULL, then binary responses
are summed directly over predicted class probabilities, whereas a default cutoff of 0.5 is used for survival probabilities. Class probability summations and survival
will appear as decimal numbers that can be interpreted as expected counts.


#### Examples
```{r}

res <- resample(Species ~ ., data = iris, model = GBMModel)
(conf <- confusion(res))
plot(conf)
```

#### Value

The return value is a ConfusionMatrix class object that inherits from table if x and y responses
are specified or a ConfusionResamples object that inherits from list if x is a Resamples object.
CoxModel 17
See Also
response, predict, resample, plot, summary
