---
title: "``MachineShop::CoxModel``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(MachineShop)
```


CoxModel Proportional Hazards Regression Model

#### Description

Fits a Cox proportional hazards regression model. Time dependent variables, time dependent strata,
multiple events per subject, and other extensions are incorporated using the counting process formulation
of Andersen and Gill.

#### Usage
<pre><code>

CoxModel(ties = c("efron", "breslow", "exact"), ...)
CoxStepAICModel(ties = c("efron", "breslow", "exact"), ...,
direction = c("both", "backward", "forward"), scope = NULL, k = 2,
trace = FALSE, steps = 1000)

</code></pre>
####Arguments

* ties character string specifying the method for tie handling.
* ... arguments passed to coxph.control.
* direction mode of stepwise search, can be one of "both" (default), "backward", or "forward".
* scope defines the range of models examined in the stepwise search. This should be a
* list containing components upper and lower, both formulae.
* k multiple of the number of degrees of freedom used for the penalty. Only k = 2 gives the genuine AIC: k = log(nobs) is sometimes referred to as BIC or SBC.
* trace if positive, information is printed during the running of stepAIC. Larger values may give more information on the fitting process.
* ``steps``:  maximum number of steps to be considered.

#### Examples
```{r}

library(survival)
library(MASS)
fit(Surv(time, status != 2) ~ sex + age + year + thickness + ulcer,
data = Melanoma, model = CoxModel())

```
Details
Response Types: Surv
Default values for the NULL arguments and further model details can be found in the source link
below.
18 dependence

#### Value

MLModel class object.
See Also
cph, coxph, coxph.control, stepAIC, fit, resample, tune
