---
title: "``MachineShop::dependence ``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(MachineShop)
```


Partial Dependence

#### Description

Calculate partial dependence of a response on select predictor variables.

#### Usage
<pre><code>

dependence(object, data = NULL, select = NULL, interaction = FALSE,
n = 10, intervals = c("uniform", "quantile"), stats = c(Mean =
base::mean))

</code></pre>
####Arguments

object MLModelFit object.
data data.frame containing all predictor variables. If not specified, the training data
will be used by default.
select expression indicating predictor variables for which to compute partial dependence
(see subset for syntax) [default: all].
interaction logical indicating whether to calculate dependence on the interacted predictors.
n number of predictor values at which to perform calculations.
intervals character string specifying whether the n values are spaced uniformly ("uniform")
or according to variable quantiles ("quantile").
stats function, one or more function names, or list of named functions with which to
aggregate the response variable over the non-selected predictor variables.

#### Value

PartialDependence class object that inherits from data.frame.
diff 19
See Also
fit, plot

#### Examples
```{r}

gbmfit <- fit(Species ~ ., data = iris, model = GBMModel)
(pd <- dependence(gbmfit, select = c(Petal.Length, Petal.Width)))
plot(pd)
```
