---
title: "``MachineShop::EarthModel ``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(MachineShop)
```
EarthModel Multivariate Adaptive Regression Splines Model

#### Description

Build a regression model using the techniques in Friedman’s papers "Multivariate Adaptive Regression
Splines" and "Fast MARS".

#### Usage
<pre><code>

EarthModel(pmethod = c("backward", "none", "exhaustive", "forward",
"seqrep", "cv"), trace = 0, degree = 1, nprune = NULL, nfold = 0,
ncross = 1, stratify = TRUE)

</code></pre>
####Arguments

* ``pmethod``:  pruning method.
trace level of execution information to display.
degree maximum degree of interaction.
nprune maximum number of terms (including intercept) in the pruned model.
nfold number of cross-validation folds.
ncross number of cross-validations if nfold > 1.
stratify logical indicating whether to stratify cross-validation samples by the response
levels.
expand.model 21
Details
Response Types: factor, numeric
Automatic Tuning Grid Parameters: nprune, degree*
* included only in randomly sampled grid points
Default values for the NULL arguments and further model details can be found in the source link
below.
In calls to varimp for EarthModel, argument metric may be specified as "gcv" (default) for the
generalized cross-validation decrease over all subsets that include each predictor, as "rss" for the
residual sums of squares decrease, or as "nsubsets" for the number of model subsets that include
each predictor. Variable importance is automatically scaled to range from 0 to 100. To obtain
unscaled importance values, set scale = FALSE. See example below.

#### Value

MLModel class object.
See Also
earth, fit, resample, tune

#### Examples
```{r}

modelfit <- fit(Species ~ ., data = iris, model = EarthModel())
varimp(modelfit, metric = "nsubsets", scale = FALSE)
