---
title: "``MachineShop::FDAModel ``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(MachineShop)
```

Flexible and Penalized Discriminant Analysis Models

#### Description

Performs flexible discriminant analysis.

#### Usage
<pre><code>

FDAModel(theta = NULL, dimension = NULL, eps = .Machine$double.eps,
method = .(mda::polyreg), ...)
PDAModel(lambda = 1, df = NULL, ...)

</code></pre>
####Arguments

theta optional matrix of class scores, typically with number of columns less than one
minus the number of classes.
dimension dimension of the discriminant subspace, less than the number of classes, to use
for prediction.
eps numeric threshold for small singular values for excluding discriminant variables.
method regression function used in optimal scaling. The default of linear regression
is provided by polyreg from the mda package. For penalized discriminant
analysis, gen.ridge is appropriate. Other possibilities are mars for multivariate
adaptive regression splines and bruto for adaptive backfitting of additive
splines. Use the . operator to quote specified functions.
... additional arguments to method for FDAModel and to FDAModel for PDAModel.
lambda shrinkage penalty coefficient.
df alternative specification of lambda in terms of equivalent degrees of freedom.
fit 23

#### Examples
```{r}

fit(Species ~ ., data = iris, model = FDAModel())
fit(Species ~ ., data = iris, model = PDAModel())
```

#### Details
Response Types: factor
Automatic Tuning Grid Parameters • FDAModel: nprune, degree*
• PDAModel: lambda
* included only in randomly sampled grid points
The predict function for this model additionally accepts the following argument.
prior prior class membership probabilities for prediction data if different from the training set.
Default values for the NULL arguments and further model details can be found in the source links
below.

#### Value

MLModel class object.
See Also
fda, predict.fda, fit, resample, tune
