---
title: "``MachineShop::fit ``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(MachineShop)
```

## Model Fitting

#### Description

Fit a model to estimate its parameters from a data set.

#### Usage
<pre><code>

fit(x, ...)
## S3 method for class 'formula'
fit(x, data, model, ...)
## S3 method for class 'ModelFrame'
fit(x, model, ...)
## S3 method for class 'recipe'
fit(x, model, ...)
24 GAMBoostModel

</code></pre>
####Arguments

x defined relationship between model predictors and an outcome. May be a ModelFrame
containing a formula, data, and optionally case weights; a formula; or a recipe.
... arguments passed to other methods.
data data.frame containing observed predictors and outcomes.
model MLModel object, constructor function, or character string naming a constructor
function that returns an MLModel object.
Details
User-specified case weights may be specified for ModelFrames upon creation with the weights
argument in its constructor.
Variables in a recipe may be used as case weights by defining a "case_weight" role for them.

#### Value

MLModelFit class object.
See Also
ModelFrame, recipe, modelinfo, tune, predict, varimp

#### Examples
```{r}

## Survival response example
library(survival)
library(MASS)
gbmfit <- fit(Surv(time, status != 2) ~ sex + age + year + thickness + ulcer,
data = Melanoma, model = GBMModel)
varimp(gbmfit)
