---
title: "``MachineShop::GLMBoostModel ``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(MachineShop)
```

 Gradient Boosting with Linear Models

#### Description

Gradient boosting for optimizing arbitrary loss functions where component-wise linear models are
utilized as base-learners.
GLMBoostModel 27

#### Usage
<pre><code>

GLMBoostModel(family = NULL, mstop = 100, nu = 0.1,
risk = c("inbag", "oobag", "none"), stopintern = FALSE,
trace = FALSE)

</code></pre>
####Arguments

family Family object. Set automatically according to the class type of the response
variable.
* ``mstop``: number of initial boosting iterations.
nu step size or shrinkage parameter between 0 and 1.
risk method to use in computing the empirical risk for each boosting iteration.
stopintern logical inidicating whether the boosting algorithm stops internally when the outof-
bag risk increases at a subsequent iteration.
trace logical indicating whether status information is printed during the fitting process.


#### Examples
```{r}

library(MASS
fit(type ~ ., data = Pima.tr, model = GLMBoostModel())
```

Details
Response Types: binary, numeric, Surv
Automatic Tuning Grid Parameters: mstop
Default values for the NULL arguments and further model details can be found in the source links
below.

#### Value

MLModel class object.
See Also
glmboost, Family, fit, resample, tune
