---
title: "``MachineShop::GLMNetModel ``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(MachineShop)
```

 GLM Lasso or Elasticnet Model

#### Description

Fit a generalized linear model via penalized maximum likelihood.

#### Usage
<pre><code>

GLMNetModel(family = NULL, alpha = 1, lambda = 0,
standardize = TRUE, intercept = NULL, penalty.factor = .(rep(1,
nvars)), standardize.response = FALSE, thresh = 1e-07,
maxit = 1e+05, type.gaussian = .(ifelse(nvars < 500, "covariance",
"naive")), type.logistic = c("Newton", "modified.Newton"),
type.multinomial = c("ungrouped", "grouped"))

</code></pre>
####Arguments

* ``family``: response type. Set automatically according to the class type of the response
variable.
* ``alpha``: elasticnet mixing parameter.
*  ``lambda``: regularization parameter. The default value lambda = 0 performs no regularization
and should be increased to avoid model fitting issues if the number of predictor variables is greater than the number of observations.
* ``standardize``: logical flag for predictor variable standardization, prior to model fitting.
intercept logical indicating whether to fit intercepts.
* ``penalty.factor``: vector of penalty factors to be applied to each coefficient.
* ``standardize.response``:
logical indicating whether to standardize "mgaussian" response variables.
* ``thresh``: convergence threshold for coordinate descent.
* ``maxit``: maximum number of passes over the data for all lambda values.
* ``type.gaussian``: algorithm type for guassian models.
* ``type.logistic``: algorithm type for logistic models.
* ``type.multinomial``: algorithm type for multinomial models.



#### Examples
```{r}

library(MASS)
fit(medv ~ ., data = Boston, model = GLMNetModel(lambda = 0.01))
````
#### Details
Response Types: factor, matrix, numeric, Surv
Automatic Tuning Grid Parameters: lambda, alpha
Default values for the NULL arguments and further model details can be found in the source link
below.

#### Value

MLModel class object.
See Also
glmnet, fit, resample, tune
