---
title: "``MachineShop::LARSModel ``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(MachineShop)
```

 Least Angle Regression, Lasso and Infinitesimal Forward Stagewise Models

#### Description

Fit variants of Lasso, and provide the entire sequence of coefficients and fits, starting from zero to
the least squares fit.

#### Usage
<pre><code>

LARSModel(type = c("lasso", "lar", "forward.stagewise", "stepwise"),
trace = FALSE, normalize = TRUE, intercept = TRUE, step = NULL,
use.Gram = TRUE)

</code></pre>
####Arguments

type model type.
trace logical indicating whether status information is printed during the fitting process.
normalize whether to standardize each variable to have unit L2 norm.
intercept whether to include an intercept in the model.
step algorithm step number to use for prediction. May be a decimal number indicating
a fractional distance between steps. If specified, the maximum number of
algorithm steps will be ceiling(step); otherwise, step will be set equal to the
source package default maximum [default: max.steps].
use.Gram whether to precompute the Gram matrix.
Details
Response Types: numeric
Automatic Tuning Grid Parameters: step
Default values for the NULL arguments and further model details can be found in the source link
below.

#### Value

MLModel class object.
See Also
lars, fit, resample, tune
LDAModel 33

#### Examples
```{r}

library(MASS)
fit(medv ~ ., data = Boston, model = LARSModel)

````
