---
title: "``MachineShop::MDAModel ``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(MachineShop)
```


 Mixture Discriminant Analysis Model

#### Description

Performs mixture discriminant analysis.

#### Usage
<pre><code>

MDAModel(subclasses = 3, sub.df = NULL, tot.df = NULL,
dimension = sum(subclasses) - 1, eps = .Machine$double.eps,
iter = 5, method = .(mda::polyreg), trace = FALSE, ...)


</code></pre>
####Arguments

subclasses numeric value or vector of subclasses per class.
sub.df effective degrees of freedom of the centroids per class if subclass centroid shrinkage
is performed.
tot.df specification of the total degrees of freedom as an alternative to sub.df.
dimension dimension of the discriminant subspace to use for prediction.
eps numeric threshold for automatically truncating the dimension.
iter limit on the total number of iterations.
method regression function used in optimal scaling. The default of linear regression is
provided by polyreg from the mda package. For penalized mixture discriminant
models, gen.ridge is appropriate. Other possibilities are mars for multivariate
adaptive regression splines and bruto for adaptive backfitting of additive
splines. Use the . operator to quote specified functions.
trace logical indicating whether iteration information is printed.
... additional arguments to mda.start and method.


#### Examples
```{r}

fit(Species ~ ., data = iris, model = MDAModel())
```

Details
Response Types: factor
Automatic Tuning Grid Parameters: subclasses
The predict function for this model additionally accepts the following argument.
prior prior class membership probabilities for prediction data if different from the training set.
Default values for the NULL arguments and further model details can be found in the source links
below.

#### Value

MLModel class object.
See Also
mda, predict.mda, fit, resample, tune
