---
title: "``MachineShop::metricinfo ``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(MachineShop)
```

 Display Performance Metric Information

#### Description

Display information about metrics provided by the MachineShop package.

#### Usage
<pre><code>

metricinfo(...)

</code></pre>
####Arguments

... one or more metric functions, function names, observed response, observed and
predicted responses, or a Resamples object. If none are specified, information
is returned on all available metrics by default.

#### Value

List of named metrics containing a descriptive "label", whether to "maximize" the metric for
better performance, the function "arguments", and supported response variable "types" for each.
See Also
metrics, resample

#### Examples
```{r}

## All metrics
metricinfo()
## Metrics by observed and predicted response types
names(metricinfo(factor(0)))
names(metricinfo(factor(0), factor(0)))
names(metricinfo(factor(0), matrix(0)))
names(metricinfo(factor(0), numeric(0)))
