---
title: "``MachineShop::NNetModel ``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(MachineShop)
``` Neural Network Model

#### Description

Fit single-hidden-layer neural network, possibly with skip-layer connections.

#### Usage
<pre><code>

NNetModel(size = 1, linout = FALSE, entropy = NULL, softmax = NULL,
censored = FALSE, skip = FALSE, rang = 0.7, decay = 0,
maxit = 100, trace = FALSE, MaxNWts = 1000, abstol = 1e-04,
reltol = 1e-08)
NNetModel 47

</code></pre>
####Arguments

size number of units in the hidden layer.
linout switch for linear output units.
* ``entropy``:  switch for entropy (= maximum conditional likelihood) fitting.
softmax switch for softmax (log-linear model) and maximum conditional likelihood fitting.
censored a variant on softmax, in which non-zero targets mean possible classes.
skip switch to add skip-layer connections from input to output.
rang Initial random weights on [-rang, rang].
decay parameter for weight decay.
maxit maximum number of iterations.
trace switch for tracing optimization.
MaxNWts maximum allowable number of weights.
abstol stop if the fit criterion falls below abstol, indicating an essentially perfect fit.
reltol stop if the optimizer is unable to reduce the fit criterion by a factor of at least
1 - reltol.
Details
Response Types: factor, numeric
Automatic Tuning Grid Parameters: size, decay
Default values for the NULL arguments and further model details can be found in the source link
below.

#### Value

MLModel class object.
See Also
nnet, fit, resample, tune

#### Examples
```{r}

library(MASS)
fit(medv ~ ., data = Boston, model = NNetModel())
```
