---
title: "``MachineShop::plot``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(MachineShop)
```


plot Model Performance Plots

#### Description

Plot measures of model performance and predictor variable importance.
plot 51

#### Usage
<pre><code>

## S3 method for class 'Performance'
plot(x, metrics = NULL, stat = base::mean,
type = c("boxplot", "density", "errorbar", "violin"), ...)
## S3 method for class 'Resamples'
plot(x, metrics = NULL, stat = base::mean,
type = c("boxplot", "density", "errorbar", "violin"), ...)
## S3 method for class 'MLModelTune'
plot(x, metrics = NULL, stat = base::mean,
type = c("boxplot", "density", "errorbar", "line", "violin"), ...)
## S3 method for class 'Calibration'
plot(x, type = c("line", "point"), se = FALSE,
...)
## S3 method for class 'Confusion'
plot(x, ...)
## S3 method for class 'ConfusionMatrix'
plot(x, ...)
## S3 method for class 'Curves'
plot(x, type = c("tradeoffs", "cutoffs"),
diagonal = FALSE, stat = base::mean, ...)
## S3 method for class 'Lift'
plot(x, find = NULL, diagonal = TRUE,
stat = base::mean, ...)
## S3 method for class 'PartialDependence'
plot(x, stats = NULL, ...)
## S3 method for class 'VarImp'
plot(x, n = NULL, ...)

</code></pre>
####Arguments

x object to plot.
metrics vector of numeric indexes or character names of performance metrics to plot.
stat function to compute a summary statistic on resampled values for MLModelTune line plots and Resamples model sorting. For Curves and Lift classes, plots are
of resampled metrics aggregated by the statistic if given or of resample-specific metrics if NULL. Curves, or NULL for resample-specific metrics.
type type of plot to construct.
... arguments passed to other methods.

se logical indicating whether to include standard error bars.
diagonal logical indicating whether to include a diagonal reference line.
find numeric true positive rate at which to display reference lines identifying the corresponding rates of positive predictions.
stats vector of numeric indexes or character names of partial dependence summary
statistics to plot.
n number of most important variables to include in the plot [default: all].
See Also
performance, resample, diff, tune, calibration, confusion, lift, dependence, varimp

#### Examples
```{r}

## Factor response example
fo <- Species ~ .
control <- CVControl()
gbmfit <- fit(fo, data = iris, model = GBMModel, control = control)
plot(varimp(gbmfit))
gbmres1 <- resample(fo, iris, GBMModel(n.trees = 25), control)
gbmres2 <- resample(fo, iris, GBMModel(n.trees = 50), control)
gbmres3 <- resample(fo, iris, GBMModel(n.trees = 100), control)
plot(gbmres3)
res <- Resamples(GBM1 = gbmres1, GBM2 = gbmres2, GBM3 = gbmres3)
plot(res)
```
