
#### ROC Curves

% What are ROC Cuves?

This type of graph is called a Receiver Operating Characteristic curve (or ROC curve.) It is a plot of the true positive rate against the false positive rate for the different possible cutpoints of a diagnostic test.

An ROC curve demonstrates several things:

It shows the tradeoff between sensitivity and specificity (any increase in sensitivity will be accompanied by a decrease in specificity).
The closer the curve follows the left-hand border and then the top border of the ROC space, the more accurate the test.
The closer the curve comes to the 45-degree diagonal of the ROC space, the less accurate the test.
The slope of the tangent line at a cutpoint gives the likelihood ratio (LR) for that value of the test. You can check this out on the graph above. Recall that the LR for T4 < 5 is 52. This corresponds to the far left, steep portion of the curve. The LR for T4 > 9 is 0.2. This corresponds to the far right, nearly horizontal portion of the curve.
The area under the curve is a measure of text accuracy.


%--------------------------------------------%
\begin{figure}
\centering
\includegraphics[width=0.4\linewidth]{./ROCcurve}
\caption{}
\label{fig:ROCcurve}
\end{figure}

%--------------------------------------------%
% http://stats.stackexchange.com/questions/24325/lorenz-curve-and-gini-coefficient-for-measuring-classifier-performance

#### The ROC Curve}
The \textbf{\textit{aSAH}} dataset summarizes several clinical and one laboratory variable of 113 patients with an aneurysmal subarachnoid hemorrhage.

```{r}
Xavier Robin, Natacha Turck, Alexandre Hainard, et al. (2011) “pROC: an open-source package for R and S+ to analyze and compare ROC curves”. BMC Bioinformatics, 7, 77. DOI: 10.1186/1471-2105-12-77
```

```{r}
> tail(aSAH)
    gos6 outcome gender age wfns s100b  ndka
136    5    Good Female  68    4  0.47 10.33
137    4    Good   Male  53    4  0.17 13.87
138    1    Poor   Male  58    5  0.44 15.89
139    5    Good Female  32    1  0.15 22.43
140    5    Good Female  39    1  0.50  6.79
141    5    Good   Male  34    1  0.48 13.45
```
%---------------------------------------------%

\item
\item
<p>
%---------------------------------------------%

```{r}
library(pROC)
data(aSAH)
# Basic example with 2 roc objects
roc1 <- roc(aSAH$outcome, aSAH$s100b)
```


```{r}
> roc1

Call:
roc.default(response = aSAH$outcome, predictor = aSAH$s100b)

Data: aSAH$s100b in 72 controls (aSAH$outcome Good) < 41 cases (aSAH$outcome Poor).
Area under the curve: 0.7314

```

%--------------------------------------------%

% plot(roc1)
% asah-roccurve

<p>
