---
title: "``MachineShop::BARTModel ``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(MachineShop)
```


 Bayesian Additive Regression Trees Model

#### Description

Flexible nonparametric modeling of covariates for continuous, binary, categorical and time-to-event
outcomes.

#### Usage
<pre><code>

BARTModel(K = NULL, sparse = FALSE, theta = 0, omega = 1,
a = 0.5, b = 1, rho = NULL, augment = FALSE, xinfo = NULL,
usequants = FALSE, sigest = NA, sigdf = 3, sigquant = 0.9,
lambda = NA, k = 2, power = 2, base = 0.95, tau.num = NULL,
offset = NULL, ntree = NULL, numcut = 100, ndpost = 1000,
nskip = NULL, keepevery = NULL, printevery = 1000)

</code></pre>
####Arguments

* K if provided, then coarsen the times of survival responses per the quantiles 1=K; 2=K; :::;K=K
to reduce computational burdern.
* sparse logical indicating whether to perform variable selection based on a sparse Dirichlet
prior rather than simply uniform; see Linero 2016.
theta, omega theta and omega parameters; zero means random.
a, b sparse parameters for Beta(a; b) prior: 0:5 <= a <= 1 where lower values
induce more sparsity and typically b = 1.
* rho sparse parameter: typically rho = p where p is the number of covariates under
consideration.
* augment whether data augmentation is to be performed in sparse variable selection.
* xinfo optional matrix whose rows are the covariates and columns their cutpoints.
* usequants whether covariate cutpoints are defined by uniform quantiles or generated uniformly.
* sigest normal error variance prior for numeric response variables.
sigdf degrees of freedom for error variance prior.
sigquant quantile at which a rough estimate of the error standard deviation is placed.
lambda scale of the prior error variance.
k number of standard deviations f(x) is away from +/-3 for categorical response
variables.
power, base power and base parameters for tree prior.
tau.num numerator in the tau definition, i.e., tau = tau:num=(k  sqrt(ntree)).
offset override for the default offset of F􀀀1(mean(y)) in the multivariate response
probability P(y[j] = 1jx) = F(f(x)[j] + offset[j]).
BlackBoostModel 11
ntree number of trees in the sum.
numcut number of possible covariate cutoff values.
ndpost number of posterior draws returned.
nskip number of MCMC iterations to be treated as burn in.
keepevery interval at which to keep posterior draws.
printevery interval at which to print MCMC progress.
Details
Response Types: factor, numeric, Surv
Default values for the NULL arguments and further model details can be found in the source links
below.

#### Value

MLModel class object.
See Also
gbart, mbart, surv.bart, fit, resample, tune

#### Examples
```{r}

library(MASS)
modelfit <- fit(medv ~ ., data = Boston, model = BARTModel())
```
