---
title: "``MachineShop::C50Model  ``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(MachineShop)
```

 13
C50Model C5.0 Decision Trees and Rule-Based Model

#### Description

Fit classification tree models or rule-based models using Quinlan’s C5.0 algorithm.

#### Usage
<pre><code>

C50Model(trials = 1, rules = FALSE, subset = TRUE, bands = 0,
winnow = FALSE, noGlobalPruning = FALSE, CF = 0.25, minCases = 2,
fuzzyThreshold = FALSE, sample = 0, earlyStopping = TRUE)

</code></pre>
####Arguments

trials integer number of boosting iterations.
rules logical indicating whether to decompose the tree into a rule-based model.
subset logical indicating whether the model should evaluate groups of discrete predictors
for splits.
bands integer between 2 and 1000 specifying a number of bands into which to group
rules ordered by their affect on the error rate.
winnow logical indicating use of predictor winnowing (i.e. feature selection).
noGlobalPruning
logical indicating a final, global pruning step to simplify the tree.
CF number in (0, 1) for the confidence factor.
minCases integer for the smallest number of samples that must be put in at least two of the
splits./
fuzzyThreshold logical indicating whether to evaluate possible advanced splits of the data.
sample value between (0, 0.999) that specifies the random proportion of data to use in
training the model.
earlyStopping logical indicating whether the internal method for stopping boosting should be
used.
Details
Response Types: factor
Automatic Tuning Grid Parameters: trials, rules, winnow
Latter arguments are passed to C5.0Control. Further model details can be found in the source link
below.
In calls to varimp for C50Model, argument metric may be spedified as "usage" (default) for the
percentage of training set samples that fall into all terminal nodes after the split of each predictor or
as "splits" for the percentage of splits associated with each predictor. Variable importance is automatically
scaled to range from 0 to 100. To obtain unscaled importance values, set scale = FALSE.
See example below.
14 calibration

#### Value

MLModel class object.
See Also
C5.0, fit, resample, tune

#### Examples
```{r}

modelfit <- fit(Species ~ ., data = iris, model = C50Model())
varimp(modelfit, metric = "splits", scale = FALSE)
```

