---
title: "``MachineShop::GBMModel  ``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(MachineShop)
```

Generalized Boosted Regression Model

#### Description

Fits generalized boosted regression models.

#### Usage
<pre><code>

GBMModel(distribution = NULL, n.trees = 100, interaction.depth = 1,
n.minobsinnode = 10, shrinkage = 0.1, bag.fraction = 0.5)

</code></pre>

#### Arguments

* distribution either a character string specifying the name of the distribution to use or a list
with a component name specifying the distribution and any additional parameters needed. Set automatically according to the class type of the response variable.
* n.trees total number of trees to fit.
* interaction.depth maximum depth of variable interactions.
* n.minobsinnode minimum number of observations in the trees terminal nodes.
* shrinkage shrinkage parameter applied to each tree in the expansion.
* bag.fraction fraction of the training set observations randomly selected to propose the next tree in the expansion.


#### Examples
```{r}

fit(Species ~ ., data = iris, model = GBMModel())
```

#### Details
* Response Types: factor, numeric, Surv
* Automatic Tuning Grid Parameters: n.trees, interaction.depth, shrinkage*, n.minobsinnode*
* included only in randomly sampled grid points
* Default values for the NULL arguments and further model details can be found in the source link
below.

#### Value

MLModel class object.
See Also
gbm, fit, resample, tune
