---
title: "``MachineShop::GLMModel   ``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(MachineShop)
```

Generalized Linear Model

#### Description

Fits generalized linear models, specified by giving a symbolic description
 of the linear predictor
and a description
 of the error distribution.

#### Usage
<pre><code>

GLMModel(family = NULL, ...)
GLMStepAICModel(family = NULL, ..., direction = c("both", "backward",
"forward"), scope = NULL, k = 2, trace = FALSE, steps = 1000)

</code></pre>
####Arguments

family description of the error distribution and link function to be used in the model.
Set automatically according to the class type of the response variable.
... arguments passed to glm.control.
direction mode of stepwise search, can be one of "both" (default), "backward", or "forward".
scope defines the range of models examined in the stepwise search. This should be a
list containing components upper and lower, both formulae.
k multiple of the number of degrees of freedom used for the penalty. Only k = 2
gives the genuine AIC: k = log(nobs) is sometimes referred to as BIC or SBC.
trace if positive, information is printed during the running of stepAIC. Larger values
may give more information on the fitting process.
* ``steps``:  maximum number of steps to be considered.
Details
Response Types: binary factor, numeric
Default values for the NULL arguments and further model details can be found in the source link
below.

#### Value

MLModel class object.
See Also
glm, glm.control, stepAIC, fit, resample, tune
GLMNetModel 29

#### Examples
```{r}

library(MASS)
fit(medv ~ ., data = Boston, model = GLMModel())
```
