---
title: "``MachineShop::KNNModel``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(MachineShop)
```

KNNModel Weighted k-Nearest Neighbor Model

#### Description

Fit a k-nearest neighbor model for which the k nearest training set vectors (according to Minkowski
distance) are found for each row of the test set, and prediction is done via the maximum of summed
kernel densities.

#### Usage
<pre><code>

KNNModel(k = 7, distance = 2, scale = TRUE, kernel = c("optimal",
"biweight", "cos", "epanechnikov", "gaussian", "inv", "rank",
"rectangular", "triangular", "triweight"))

</code></pre>
####Arguments

k numer of neigbors considered.
distance Minkowski distance parameter.
scale logical indicating whether to scale predictors to have equal standard deviations.
kernel kernel to use.
Details
Response Types: factor, numeric, ordinal
Automatic Tuning Grid Parameters: k, distance*, kernel*
* included only in randomly sampled grid points
Further model details can be found in the source link below.

#### Value

MLModel class object.
See Also
kknn, fit, resample, tune

#### Examples
```{r}

fit(Species ~ ., data = iris, model = KNNModel())
``` 
