---
title: "``MachineShop::MLModel  ``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(MachineShop)
```

 MLModel Class Constructor

#### Description

Create a model for use with the MachineShop package.

#### Usage
<pre><code>

MLModel(name = "MLModel", label = name, packages = character(),
types = character(), params = list(), grid = function(x, length,
random, ...) NULL, design = c(NA, "model.matrix", "terms"),
fit = function(formula, data, weights, ...) stop("no fit function"),
predict = function(object, newdata, times, ...)
stop("no predict function"), varimp = function(object, ...) NULL, ...)

</code></pre>
####Arguments

name character string name for the instantiated MLModel object; same name as the
object to which the model is assigned.
label descriptive label for the model.
packages character vector of packages whose namespaces are required by the model.
types character vector of response variable types to which the model can be fit. Supported
types are "binary", "factor", "matrix", "numeric", "ordered", and
"Surv".
params list of user-specified model parameters to be passed to the fit function.
grid tuning grid function whose first agument x is a ModelFrame of the model fit data
and formula, followed by a length to use in generating sequences of parameter
values, a number of grid points to sample at random, and an ellipsis (...).
design character string indicating whether the type of design matrix used to fit the
model is a "model.matrix", a data.frame of the original predictor variable
"terms", or unknown (default).
fit model fitting function whose arguments are a formula, a data frame, case
weights, and an ellipsis.
MLModel 43
predict model prediction function whose arguments are the object returned by fit,
a newdata frame of predictor variables, optional vector of times at which to
predict survival, and an ellipsis.
varimp variable importance function whose arguments are the object returned by fit,
optional arguments passed from calls to varimp, and an ellipsis.
... arguments passed from other methods.
Details
If supplied, the grid function should return a list whose elements are named after and contain values
of parameters to include in a tuning grid to be constructed automatically by the package.
Values returned by the predict functions should be formatted according to the response variable
types below.
factor a vector or column matrix of probabilities for the second level of binary factors or a matrix
whose columns contain the probabilities for factors with more than two levels.
matrix a matrix of predicted responses.
numeric a vector or column matrix of predicted responses.
Surv a matrix whose columns contain survival probabilities at times if supplied or a vector of
predicted survival means otherwise.
The varimp function should return a vector of importance values named after the predictor variables
or a matrix or data frame whose rows are named after the predictors.

#### Value

MLModel class object.
See Also
modelinfo, fit, resample, tune

#### Examples
```{r}

## Logistic regression model
LogisticModel <- MLModel(
name = "LogisticModel",
types = "binary",
fit = function(formula, data, weights, ...) {
glm(formula, data = data, weights = weights, family = binomial, ...)
},
predict = function(object, newdata, ...) {
predict(object, newdata = newdata, type = "response")
},
varimp = function(object, ...) {
pchisq(coef(object)^2 / diag(vcov(object)), 1)
}
)
44 ModelFrame
library(MASS)
res <- resample(type ~ ., data = Pima.tr, model = LogisticModel)
summary(res)
```
