---
title: "``MachineShop::RandomForestModel``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(MachineShop)
```

 Random Forest Model

#### Description

Implementation of Breiman’s random forest algorithm (based on Breiman and Cutler’s original
Fortran code) for classification and regression.

#### Usage
<pre><code>

RandomForestModel(ntree = 500, mtry = .(if (is.factor(y))
floor(sqrt(nvars)) else max(floor(nvars/3), 1)), replace = TRUE,
nodesize = .(if (is.factor(y)) 1 else 5), maxnodes = NULL)

</code></pre>

####Arguments

* ntree number of trees to grow.
* mtry number of variables randomly sampled as candidates at each split.
* replace should sampling of cases be done with or without replacement?
* nodesize minimum size of terminal nodes.
* maxnodes maximum number of terminal nodes trees in the forest can have.

#### Examples
```{r}

library(MASS)
fit(medv ~ ., data = Boston, model = RandomForestModel())
```

#### Details
Response Types: factor, numeric
Automatic Tuning Grid Parameters: mtry, nodesize*
* included only in randomly sampled grid points
Default values for the NULL arguments and further model details can be found in the source link
below.

#### Value

MLModel class object.
See Also
randomForest, fit, resample, tune
